Actuator line modeling of vertical-axis turbines

### 2016-05-13 paper.tex
Don't end sentence with two periods
Remove some intermediate equations from end effects section

A correction for added mass effects, or the effects due to accelerating the
fluid, was taken from Strickland et al.~\cite{Strickland1981}, which was derived
by considering a pitching flat plate in potential flow. In the blade element
coordinate system, the normal and chordwise (pointing from trailing to leading
edge, which is opposite the $x$-direction used by Strickland et al.)
coefficients due to added mass are
\begin{equation}
    C_{n_\mathrm{AM}} = -\frac{\pi c \dot{U_n}}{8 | U_\mathrm{rel} |^2},
\end{equation}
and
\begin{equation}
    C_{c_\mathrm{AM}} = \frac{\pi c \dot{\alpha} U_n }{8 | U_\mathrm{rel} |^2},
\end{equation}
respectively, where $U_n$ is the normal component of the relative velocity, and
dotted variables indicate time derivatives, which were calculated using a simple
first order backward finite difference. Similarly, the quarter-chord moment
coefficient due to added mass was calculated as
\begin{equation}
    C_{m_\mathrm{AM}} = -\frac{C_{n_\mathrm{AM}}}{4}
        - \frac{U_n U_c}{8 | U_\mathrm{rel} |^2},
\end{equation}
where $U_c$ is the chordwise component of relative velocity. Note that the
direction of positive moment is ``nose-up,'' which is opposite that used by
Strickland et al..

@@

From Prandtl's lifting line theory, the geometric angle of attack $\alpha$ of a
foil with an arbitrary circulation distribution can be expressed as a function
of nondimensional span $\theta$ as \cite{Anderson2001}
\begin{equation}
    \alpha (\theta) = \frac{2S}{\pi c (\theta)}
    \sum_1^N A_n \sin \theta
    + \sum_1^N n A_n \frac{\sin n \theta}{\sin \theta}
    + \alpha_{L = 0}(\theta),
    \label{eq:lifting-line}
\end{equation}
where $S$ is the span length, $c(\theta)$ is the chord length, and $N$ is the
number of locations or elements sampled along the foil. This relationship can be
rearranged into a matrix equation to solve for the unknown Fourier coefficients
$A_n$,
\begin{equation}
    [\alpha_m ] - \alpha_{L=0} = [D_{mn}][A_n],
\end{equation}
where
\begin{equation}
    D_{mn} = \sum_1^N \left[ \frac{2b}{\pi c_m} \sin n \theta_m + n \frac{\sin n
        \theta_m}{\sin \theta_m} \right].
\end{equation}

With the Fourier coefficients, the circulation distribution can be calculated as
\begin{equation}
    \Gamma (\theta) = 2SU_\infty \sum_1^N A_n \sin n \theta,
\end{equation}
which, via the Kutta--Joukowski theorem, provides the lift coefficient
distribution
\begin{equation}
    C_l(\theta) = \frac{-\Gamma (\theta)}{\frac{1}{2} c U_\infty}.
\end{equation}

>>>>

A correction for added mass effects, or the effects due to accelerating the
fluid, was taken from Strickland et al.~\cite{Strickland1981}, which was derived
by considering a pitching flat plate in potential flow. In the blade element
coordinate system, the normal and chordwise (pointing from trailing to leading
edge, which is opposite the $x$-direction used by Strickland et al.)
coefficients due to added mass are
\begin{equation}
    C_{n_\mathrm{AM}} = -\frac{\pi c \dot{U_n}}{8 | U_\mathrm{rel} |^2},
\end{equation}
and
\begin{equation}
    C_{c_\mathrm{AM}} = \frac{\pi c \dot{\alpha} U_n }{8 | U_\mathrm{rel} |^2},
\end{equation}
respectively, where $U_n$ is the normal component of the relative velocity, and
dotted variables indicate time derivatives, which were calculated using a simple
first order backward finite difference. Similarly, the quarter-chord moment
coefficient due to added mass was calculated as
\begin{equation}
    C_{m_\mathrm{AM}} = -\frac{C_{n_\mathrm{AM}}}{4}
        - \frac{U_n U_c}{8 | U_\mathrm{rel} |^2},
\end{equation}
where $U_c$ is the chordwise component of relative velocity. Note that the
direction of positive moment is ``nose-up,'' which is opposite that used by
Strickland et al.

@@

From Prandtl's lifting line theory, the geometric angle of attack $\alpha$ of a
foil with an arbitrary circulation distribution can be expressed as a function
of nondimensional span $\theta$ as \cite{Anderson2001}
\begin{equation}
    \alpha (\theta) = \frac{2S}{\pi c (\theta)}
    \sum_1^N A_n \sin \theta
    + \sum_1^N n A_n \frac{\sin n \theta}{\sin \theta}
    + \alpha_{L = 0}(\theta),
    \label{eq:lifting-line}
\end{equation}
where $S$ is the span length, $c(\theta)$ is the chord length, and $N$ is the
number of locations or elements sampled along the foil. This relationship can be
rearranged into a matrix equation to solve for the unknown Fourier coefficients
$A_n$, after which the circulation distribution can be calculated as
\begin{equation}
    \Gamma (\theta) = 2SU_\infty \sum_1^N A_n \sin n \theta,
\end{equation}
which, via the Kutta--Joukowski theorem, provides the lift coefficient
distribution
\begin{equation}
    C_l(\theta) = \frac{-\Gamma (\theta)}{\frac{1}{2} c U_\infty}.
\end{equation}
